Greedy Heuristics for Solving the Weighted Orthogonal Art Gallery Problem

### 2020-09-07 doc/paper.tex
small fix
extended the doc

      One additional criterion can be given as a measure of intersection between one set  $S_{p_i}$ and 
      and the other sets $S_{p_j}$, $j \neq i$ as follow:
      \begin{align}\label{eq:intersection-heuristic}
      	   g(s^P,p_i) = \frac{\sum_{p_j \in V \setminus s^P: p_i \neq p_j}|S_{p_i} \cap S_{p_j}|}{|V|-|s^P|-1}, p_i \in V \setminus s^P,
      \end{align}
      where $|S_{p_i} \cap S_{p_j}|$ denotes the measure of surface (in some unit) of the intersection for the two 
      visible regions. If some set $S_{p_i}$ has less intersection with the  visible regions of other candidate guards it is more likely that $p_i$ will be a good candidate for a guard. So, based on it, we try to always add a vertex $p_j$ to $s^P$ which has the smallest $g$ value acc. to formula~(\ref{eq:intersection-heuristic})

@@

     \subsection{Beam Search (BS)}
        Beam Searxh is an incomplete BFS heuristic search algorithm. At each level of the search, the best $\beta>0$ nodes i kept in the structure called \emph{beam} $B$. all nodes are then expanded in all possible ways. Among the expansions, again, $\beta$ bst nodes is taken for the beam of the next level. 
        The search is processed in the same manner until $B$ is empty. The main question concerns of the criterion of choosing the nodes for a beam. This is done by means of a heuristic evaluation of the nodes. The heuristic is a problem-specific aspect of each problem that is considered for solving. \fxnote{work in progress...}
    \end{comment}   
     \section{Computational Results}
       We used the instance of a specific OAGP and assigned the weights to each vertex of polygons. We have generated three kind of benchmarks:
       \begin{itemize}
       	  \item \emph{random benchmarks}. For each vertex $i$ of polygon $P$ we take a random value $w_i \in \{X_1,...,X_q\}$ \fxnote{da li je domen ovdje OK? } as its weight ($X_i$ are some random values for prices), $q \in \mathbb{N}$.
       	  \item \emph{topologically-based benchmarks}. For each vertex $i$ of polygon $P$ let us denote by $l_i$ and $l_{i+1}$ the lengths of edges that comes out of vertex $i$. Then, $w_i := \frac{l_i + l_{i+1}}{2}$. This can be augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that vertex is a guard can see a larger pieces of polygon $P$. This implies that the range of camera $i$ has to be larger, which again means that it has to be of a higher price.
       	 \item \emph{distance-based benchmarks:} For each vertex $i$, a weight is assigned to $i$ by making use of the information about the distance from that point to the point in the polygon which is at the longest distance but visible from $i$ (among all other points in polygon).  
       \end{itemize}
     \section{Conclusions and Future Work}

>>>>

      One additional criterion can be given as a measure of intersection between one set  $S_{p_i}$ and 
      and the other sets $S_{p_j}$, $j \neq i$ as follow:
      \begin{align}\label{eq:intersection-heuristic}
      	   g(s^P,p_i) = \frac{\sum_{p_j \in V \setminus s^P: p_i \neq p_j}|S_{p_i} \cap S_{p_j}|}{|V|-|s^P|-1}, p_i \in V \setminus s^P,
      \end{align}
      where $|S_{p_i} \cap S_{p_j}|$ denotes the measure of surface (in some unit) of the intersection for the two 
      visible regions. If some set $S_{p_i}$ has less intersection with the  visible regions of other candidate guards it is more likely that $p_i$ will be a good candidate for a guard. So, based on it, we always try to  add a vertex $p_j$ to $s^P$ which has the smallest $g$ value acc. to formula~(\ref{eq:intersection-heuristic})

@@

     \subsection{Beam Search (BS)}
        Beam Searxh is an incomplete BFS heuristic search algorithm. At each level of the search, the best $\beta>0$ nodes i kept in the structure called \emph{beam} $B$. all nodes are then expanded in all possible ways. Among the expansions, again, $\beta$ bst nodes is taken for the beam of the next level. 
        The search is processed in the same manner until $B$ is empty. The main question concerns of the criterion of choosing the nodes for a beam. This is done by means of a heuristic evaluation of the nodes. The heuristic is a problem-specific aspect of each problem that is considered for solving. \fxnote{work in progress...}
    \end{comment}   
     \section{Computational Results}
       We used the instance of a specific OAGP and assigned the weights to each vertex of polygons. We have generated three kind of benchmarks:
       \begin{itemize}
       	  \item \emph{random benchmarks}. For each vertex $i$ of polygon $P$ we take a random value $w_i \in \{X_1,...,X_q\}$ \fxnote{da li je domen ovdje OK? } as its weight ($X_i$ are some random values for prices), $q \in \mathbb{N}$.
       	  \item \emph{topologically-based benchmarks}. For each vertex $i$ of polygon $P$ let us denote by $l_i$ and $l_{i+1}$ the lengths of edges that comes out of vertex $i$. Then, $w_i := \frac{l_i + l_{i+1}}{2}$. This can be augmented by the fact that if the the arithmetic length of both edges that comes out of vertex $i$ is longer, it is expected that vertex is a guard can see a larger pieces of polygon $P$. This implies that the range of camera $i$ has to be larger, which again means that it has to be of a higher price.
       	 \item \emph{distance-based benchmarks:} For each vertex $i$, a weight is assigned to $i$ by making use of the information about the distance from that point to the point in the polygon which is at the longest distance but visible from $i$ (among all other points in polygon). 
       	 \item \emph{point-based benchmarks:} For each vertex $j$, we are looking for the number of points in D(P) that are visible from the given vertex $(|V(j)|)$. Based on this measure, we assign prices to the vertices. If |V(j)| is larger, the large is the price of the vertex $j$.
       \end{itemize}
     \section{Conclusions and Future Work}
